A Data-Driven Framework for Neural Field Modeling

### 2011-01-18 ltx/first_order_framework/response_to_reviews.tex

    \begin{enumerate}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.

		\emph{We have added to the results section describing experiment II: `These results indicate that the solution to the system may not be unique in non-ideal, practical situations. Nevertheless, the net shape of the connectivity kernel can be determined reasonably accurately.'}

        \item The use of Euler discretisation and how this affects the system's behavior.

		\emph{We have added some comments to  Appendix A, where the discretization is performed.  We have also added a reference for the further analysis of the error introduced by Euler discretization method along with a reference for an alternative method.}

### 2011-01-18 ltx/first_order_framework/response_to_reviews.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{soul}
\usepackage{anysize} %<-for setting margins
\marginsize {1.6cm}{1.6cm}{2.0cm}{2cm}
\usepackage{color}
\newcommand{\dean}[1]{\textcolor{red}{#1}}
\newcommand{\mike}[1]{\textcolor{green}{#1}}
\newcommand{\parham}[1]{\textcolor{blue}{#1}}

\title{Responses - A Data-Driven Framework for Neural Field Modeling}
\author{D. Freestone, P. Aram, M. Dewar, K. Scerri, D. Grayden, V. Kadirkamanathan}

\begin{document}
    \maketitle

    The authors would very much like to thank the reviewers for their encouraging comments and their efforts to help improve this paper. Please find below the authors responses to the reviewers questions and suggestions regarding the manuscript. 
\\

@@

\emph{A few comments have been added to the last paragraph of the `Extensions to the Framework' section of the discussion.}

\item Figure 4. Should the axes be indicated as spatial frequency rather than just Hz?

\emph{Yes. Axes of Figure 4. (and also Figure 5.) are now changed to spatial frequency. The unit of the spatial frequency within the text is changed to cycles/mm.}

\item Page 45, Appendix D (now Appendix E), Par 1, line 6: should `transform of a n-' should be `transform of an n-' ? I am grammatically challenged perhaps.

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
minor change for reviewer2 comment11

Note, the discretization using the first order Euler method has the potential to affect the system's behaviour, where the difference between the continuous and discrete-time systems can potentially be substantial. The Euler method was used for its simplicity. The sampling period of 1~ms was used in this paper, which yielded a stable discrete-time system and good estimation results. An analysis of the error introduced by Euler discretization method can be found in~\citet{Butcher2008}. An alternative to Euler's method is the local linearization method~\citep{Ozaki1994}.

>>>>

Note, the discretization using the first order Euler method has the potential to affect the system's behaviour in terms of both stability and consistency, an analysis of the error introduced by Euler discretization method can be found in~\citet{Butcher2008}. The Euler method was used for its simplicity. The sampling period of 1~ms was used in this paper, which yielded a stable discrete-time system and good estimation results.  An alternative to Euler's method is the local linearization method~\citep{Ozaki1994}.

% Note, the discretization using the first order Euler method has the potential to affect the system's behaviour, where the difference between the continuous and discrete-time systems can potentially be substantial. The Euler method was used for its simplicity. The sampling period of 1~ms was used in this paper, which yielded a stable discrete-time system and good estimation results. An analysis of the error introduced by Euler discretization method can be found in~\citet{Butcher2008}. An alternative to Euler's method is the local linearization method~\citep{Ozaki1994}.
